On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-05-11 Manuscript/manuscript.tex
Have gone through more of Prof Schifano's suggestions

Devon Allen, an alumnus of the University of Oregon in 
Eugene, Oregon, was
expected to be a contender for the 2022 World Track and Field Championships 110 
meter hurdle.  After running the event in 12.84 seconds in early June 2022 
(only 0.04 seconds away from the world record \citep{wa2022preview}) and coming 
in third at the United States Track and Field 
Championships also in Eugene in late June, Allen was poised to compete in the 
2022 World Track and Field Championships at the same Eugene venue in August.
%After coming in third in the 110 meter hurdles at the United States Track and 
%Field Championships also in Eugene at the end of June, Allen was poised to 
%compete in the 2022 World Track and Field Championships also 
%located at Eugene in August.
%two months later. 
At the World Championships, Allen made it through the preliminary
heats and semifinals to reach the final heat while posting reaction times of 
0.123 in his preliminary heat and 0.101 in his semifinal.  
%Allen, who attended the University of Oregon also in Eugene, 
%(the location of US World Championship 
%\eds{US World? remove World?} and the World Championship) 
%was
%considered to be a favorite for the 110 meter hurdle after running 12.84 seconds
%in early June; only 0.04 seconds away from the world record \citep{wa2022preview}.
%Thus 
His disqualification in the final heat by reacting in 0.099 seconds instead of 
0.1 was met
with shock from both Allen and fans alike.  NBC, who was broadcasting the
championships in the United States, later uploaded a video to their YouTube
channel that showed the disqualification; it can be found here:
\url{https://www.youtube.com/watch?v=D6NXTMo-1yM}. The crowd erupted with jeers 
when they found out that Allen was disqualified, angry at the result.  Had Allen 
reacted just 0.001 seconds slower he would have been allowed to compete and been 
spared waiting until the next World Track and Field Championships.

%2)
Allen's disqualification has been discussed extensively in online communities
such as \url{www.LetsRun.com}, a website that is part message board and part
news. The message board,
which functions similarly to Reddit, is very active during important running
events, including during the finals of major events such as
the Olympics and the World Track and Field Championships.  However, it is the
news section of the website that generated articles such as \citet{johnson2022data}
and \citet{johnson2022was} from  Robert Johnson, who created and runs 
the LetsRun website.  He argued that there was an error
with the timing equipment at the 2022 World Track and Field Championship and
cited graphs, computed simple statistics such as median reaction times, and 
compared the reaction times at the 2022 World Track and Field Championship to 
other competitions
such as the United States Track and Field Championships and other World Championships.
The comparisons lacked formal statistical analysis, however. 
The alleged 99.95\% chance Allen was wronged 
came from Johnson claiming there is a $(1/13)^3$ chance that the fastest 
reaction times over the past 13 competitions of the men's 100 meter, men's 110 
meter hurdle, and women's 100 meter would all come from the same championship 
\citep{johnson2022was}.
%came from Johnson claiming there is a $(1/13)^3$ chance that the fastest 
%reaction times came during the same championship for the men's 100 meter,
%men's 110 meter hurdle, and women's 100 meter for 13 competitions held between 2003 and 2022 
%\of{Cleaned up but may need additional work}
\of{Cleaned this up a little but still a little messy.}
\eds{is this better? (and still correct?)}

@@

%4)
The objective to this paper is to analyze the reaction times at the 2022 World 
Track and Field Championship to check for any abnormalities, and we approach
this two different ways.  First we model the data, which is
the reaction times of every non-disqualification since the 1999 World 
Championships, using a gamma linear mixed-effects model with a random effect 
accounting for the venue (or year). 
%\eds{are you using covariates?  Data section
%implies that you are, but Results section does not}
%\of{Cleaned up confusion about covariates, but no none were used in the paper} 
Based on the fitted model, we can then estimate the probability of a reaction 
time being below a certain threshold (e.g., 0.1). 
Second, we compare reaction times for athletes who have competed
at additional competitions to the 2022 World Track and Field Championship.  By
comparing reaction times from the same athlete across multiple competitions we 
are able to determine if the 2022 data differed significantly from other 
competitions.
Our investigation into reaction times is important not only because if its
implications for future races, but also because reaction times have
been shown to affect the overall time of the race \citep{delalija2008reaction}.
Thus, faster reaction times lead to faster overall times; which is the goal of
every sprinter who steps onto the track.
%\eds{I recommend moving the rest of this paragraph to Section 2.2 as I don't
%think it is critical for readers to know all the details here.}
%First we can compare the reaction times of athletes who
%competed at the World Track and Field Championship in both 2019 and 2022, and 
%second we can compare how athletes performed at the 2022 championship relative 
%to their national/qualifiers meet. In order to reduce any chances
%of athletes improving reaction time, we can also look at data from qualifying meets.
%Almost every athlete had to qualify by proving they are elite at the national level, 
%usually by coming in at least fourth. Thus, data was compiled on athletes who competed
%at the 2022 World Track and Field Championships on what these athletes also ran 
%at their country's national championship. If there was any argument that athletes
%have improved their reaction time from 2019 to 2022, it should now be considered
%nearly null, as the national competitions took place between June and July 2022 
%and the World Championships were in August. The equipment used to measure reaction
%time cannot be guaranteed to be the same from national to international
%competition, but the time span between meets has been reduced considerably.

@@

There are two types of data that are explored throughout this paper: data from
1999-2022 for every world championship, and data from athletes who competed in
the 2022 World Championships and another competition (either 2019 World 
Championships or a 2022 national competition typically held within three months 
of the 2022 World Championships). 
\eds{is this true? are you still using the 2019 world championships data for the
rank-based analyses, or only the national competitions?}
The first data set is used for the GLMM analyses described in 
Section~\ref{sec:glmm}, while the second collection of data is used for the 
rank-based comparisons described in Section~\ref{sec:rank}.

@@

\eds{I wonder if this paragraph would be better placed in the introduction?}
\of{I think it could fit in the brief section between the start of the Data section
and the GLMM subsection in the paragraph starting with "There are two types..."}
Something that is extremely important to note in the data is the inconsistency 
of World Athletics in terms of how they penalize false starts.  From 2007--2009,
the IAAF (the former name for World Athletics, and the governing body for the 
World Track and Field Championships) instituted a rule change that allowed one 
warning false start before a sprinter was disqualified \citep{iaaf2009falsestart}. 
This was desirable for World Athletics as false starts can make already long 
track meets more tedious, both for athletes and viewers watching the television 
broadcast.  There were 18 male and 7 female false starts at the 2007 World 
Championships, and 18 male and 7 female starts at the 2009 World Championships. 
Starting in 2011, the rule was scrapped, and the old policy which automatically 
disqualifies runners who false start was reinstated. By returning to the harsher 
policy and cracking down on false starts, World Athletics had reduced men's 
false starts by two thirds in 2011 (6 male and 4 female disqualifications) 
\citep{iaaf2009falsestart}.
%The effect? At the 2011 
%World Championship there were 6 male disqualifications and 4 female 
%disqualifications \citep{iaaf2009falsestart}.  
%One study that looked at different false start rules that IAAF has
%imposed from 1997 to 2009 and found that the reaction times when there was less 
%leniency improved by a statistically significant amount
%\citep{haugen2013effect}. 
\citet{haugen2013effect} examined the effect of different false start
rules that IAAF has imposed from 1997 to 2009 and found statistically 
significant improvement in reaction times under more lenient rules.
  %\eds{I am not sure the previous sentence follows from the one preceding it. Why
% does World Athletics find faster reaction times desirable?  Do you mean that
%they find fewer false starts desirable?}

@@

\subsection{Beyond World Championships}\label{sec:databeyond}
The motivation for looking beyond World Championships data came from an 
exploratory analysis examining how United States athletes reacted at the 
2022 United States Track and Field Championships.
%\eds{be consistent with how you refer to the US championship:
%``United States Track and Field Championships" and ``United States Track and Field 
%Championships" are both being used; please pick one and use that throughout}
%\of{Resolved; changed all USA to United States.}
From June 23-26 2022, the United States held its Track
and Field Championships at Hayward 
Field in Eugene, Oregon to decide who to send to the World Championships 
being held at the same venue in August. %the exact same venue as used 
%for the World Track and Field Championship a month later.  
%Thus, a baseline is able to be established for the four United States athletes who 
Thus, we can establish a baseline for the four United States athletes who 
competed in at least one round of both events: Trey Cunningham, Daniel Roberts, 
Grant Holloway, and Devon Allen. Every athlete reacted faster in all the World 
Track and Field Championship races compared to the United States Track and Field 
Championship races. Devon Allen raced three times at the United States Track and
Field Championship and three times at the World Track and Field Championships. 
His reaction times were substantially faster in the World Track and
Field Championships compared to the United States Track and Field Championships 
as were his
teammates. 
This comparison suggests that the timing system used between the two
meets may have been meaningfully different to the point where Devon Allen was
disqualified more because of faulty equipment rather than because he reacted
too quickly.  Table~\ref{fig:USAvsWorld} highlights the difference in reaction 
times for Devon Allen, Trey Cunningham, Grant Holloway, and Daniel Roberts. 
%``United States" denotes
%the United States Track and Field Championships, ``World" denotes the World Track and Field
%Championships. All numbers listed in the table are the reaction
%time for the respective athletes in seconds.

@@

The %World Championship data and the data eyond the World Championship 
data described in Sections~\ref{sec:dataworld} and~\ref{sec:databeyond} were
analysed with GLMM and rank-based methods, respectively.
\eds{need consistency with ``Championship" or ``Championships - I am not sure 
which one is correct.  I am using Championships (plural) but
change everything to singular if that is preferred}

@@

%% In this case, athletes who have more
%% data are generally thought to be faster, as they have made it further in the
%% competition.  Clusters range from two to six, with two indicating that at each
%% competition they only made it to the heats, but a cluster size of six indicates
%% that they made the finals in both competitions.  While the number of times
%% athletes compete is based off their overall time not their reaction time, the
%% two are correlated \citep{delalija2008reaction}.
%% Group is either designated to be 1 or 2, with 1 corresponding to either the
%% national level data or the previous world championship data and 2 corresponding
%% to the 2022 data.

@@

%Citation needed in this section
Since 1985 Seiko Holding Corporations has served every World Athletics 
Championship as the official timer \citep{wa2022seiko}.  Since 1985, the 
technology and the ability
to accurately predict measurements: long jump distances, false starts, total 
time, reaction time, etc. have all dramatically improved.  Seiko did not start 
tracking reaction time as an official measurement until 1999 in the men's and 
women's 100 meter \eds{110 for men?} hurdles. 
Seiko regularly updates their equipment so that they provide cutting edge
technology to the World Track and Field Championships, the highest stakes in the 
world of running outside of the Olympics. Seiko's technology for detecting 
reaction times relies on the pressure that athletes exert on the plate when they 
push off.  Their systems measure the time differential
between when the ``gun" goes off to start the race and when the pressure changes 
\citep{wa2022seiko}.  If an athlete has a reaction time under 0.1 seconds, it 
is deemed a 
false start as it is considered that no athlete can react so quickly 
\citep{Seiko-Timing}.  Thus, a reaction time of for example 0.05, suggests that 
the athlete predicted the gun and it was luck that caused their abnormally high 
time.  At the World Championships level, World Athletics and Seiko want to remove 
that element of luck and thus impose the 0.1 second barrier. In 2013, Seiko 
upgraded their timing equipment for sprinting events (110 meter hurdles falls 
under this category) \citep{wa2013backtage}. Since 1999, the
slowest \eds{highest as in fastest or slowest? Neither seems consistent with 
the boxplots in Figure 1} \of{Resolved} reaction 
times in the men's 110-meter hurdle were recorded in 2013.  That is not to say
 that the higher 
times were caused by Seiko's equipment, but the two may be related.  It is worth 
noting that prior
to 2022, Seiko again upgraded its technology but for its jump management system.
\eds{I would argue that this paragraph should go in the discussion as there are 
no results presented here}

@@

It is worth noting that in the semifinals of the 2022 World Track and
Field Championships, Allen's reaction time was 0.101 which is only 0.001 above
the legal limit. What this suggests is that Allen may have strong reflexes
and be able to react extremely well to the sound of the gun. It seems unlikely 
that Allen would be able to correctly predict the gun with such precision two 
times in a row, which is the exact reason that the 0.1 second reaction time 
disqualification barrier was
imposed in the first place. Allen showed at the Championship he was able to
react extremely fast two times, which may suggest skill rather than luck. Devon 
Allen is a very good athlete, as evidenced by his football career at the 
University of Oregon
and making it onto the Philadelphia Eagles practice squad this past year 
\citep{hurley2022eagles}. Thus, the 0.099 reaction time may not have been 
a product of Devon Allen predicting the start of the race but rather a 
combination of a quick reaction and a possibly faulty sensor.

>>>>

Devon Allen, an alumnus of the University of Oregon in 
Eugene, Oregon, was
expected to be a contender for the 2022 World Track and Field Championships 110 
meter hurdle.  After running the event in 12.84 seconds in early June 2022 
(only 0.04 seconds away from the world record \citep{wa2022preview}) and coming 
in third at the United States Track and Field 
Championships also in Eugene in late June, Allen was poised to compete in the 
2022 World Track and Field Championships at the same Eugene venue in August.
%After coming in third in the 110 meter hurdles at the United States Track and 
%Field Championships also in Eugene at the end of June, Allen was poised to 
%compete in the 2022 World Track and Field Championships also 
%located at Eugene in August.
%two months later. 
At the World Championships, Allen made it through the preliminary
heats and semifinals to reach the final heat while posting reaction times of 
0.123 in his preliminary heat and 0.101 in his semifinal.  
%Allen, who attended the University of Oregon also in Eugene, 
%(the location of US World Championships 
%\eds{US World? remove World?} and the World Championship) 
%was
%considered to be a favorite for the 110 meter hurdle after running 12.84 seconds
%in early June; only 0.04 seconds away from the world record \citep{wa2022preview}.
%Thus 
His disqualification in the final heat by reacting in 0.099 seconds instead of 
0.1 was met
with shock from both Allen and fans alike.  NBC, who was broadcasting the
championships in the United States, later uploaded a video to their YouTube
channel that showed the disqualification; it can be found here:
\url{https://www.youtube.com/watch?v=D6NXTMo-1yM}. The crowd erupted with jeers 
when they found out that Allen was disqualified, angry at the result.  Had Allen 
reacted just 0.001 seconds slower he would have been allowed to compete and been 
spared waiting until the next World Track and Field Championships.

%2)
Allen's disqualification has been discussed extensively in online communities
such as \url{www.LetsRun.com}, a website that is part message board and part
news. The message board,
which functions similarly to Reddit, is very active during important running
events, including during the finals of major events such as
the Olympics and the World Track and Field Championships.  However, it is the
news section of the website that generated articles such as \citet{johnson2022data}
and \citet{johnson2022was} from  Robert Johnson, who created and runs 
the LetsRun website.  He argued that there was an error
with the timing equipment at the 2022 World Track and Field Championships and
cited graphs, computed simple statistics such as median reaction times, and 
compared the reaction times at the 2022 World Track and Field Championships to 
other competitions
such as the United States Track and Field Championships and other World Championships.
The comparisons lacked formal statistical analysis, however. 
The alleged 99.95\% chance Allen was wronged 
came from Johnson claiming there is a $(1/13)^3$ chance that the fastest 
reaction times over the past 13 competitions of the men's 100 meter, men's 110 
meter hurdle, and women's 100 meter would all come from the same year. 
\citep{johnson2022was}.
%came from Johnson claiming there is a $(1/13)^3$ chance that the fastest 
%reaction times came during the same championships for the men's 100 meter,
%men's 110 meter hurdle, and women's 100 meter for 13 competitions held between 2003 and 2022 
%\of{Cleaned up but may need additional work}
\of{Cleaned this up a little but still a little messy.}
\eds{is this better? (and still correct?)}
\of{Yes, I think it looks good}

@@

%4)
The objective to this paper is to analyze the reaction times at the 2022 World 
Track and Field Championships to check for any abnormalities, and we approach
this two different ways.  First we model the data, which is
the reaction times of every non-disqualification since the 1999 World 
Championships, using a gamma linear mixed-effects model with a random effect 
accounting for the venue (or year). 
%\eds{are you using covariates?  Data section
%implies that you are, but Results section does not}
%\of{Cleaned up confusion about covariates, but no none were used in the paper} 
Based on the fitted model, we can then estimate the probability of a reaction 
time being below a certain threshold (e.g., 0.1). 
Second, we compare reaction times for athletes who have competed
at additional competitions to the 2022 World Track and Field Championship.  By
comparing reaction times from the same athlete across multiple competitions we 
are able to determine if the 2022 data differed significantly from other 
competitions.
Our investigation into reaction times is important not only because if its
implications for future races, but also because reaction times have
been shown to affect the overall time of the race \citep{delalija2008reaction}.
Thus, faster reaction times lead to faster overall times; which is the goal of
every sprinter who steps onto the track.
%\eds{I recommend moving the rest of this paragraph to Section 2.2 as I don't
%think it is critical for readers to know all the details here.}
%First we can compare the reaction times of athletes who
%competed at the World Track and Field Championships in both 2019 and 2022, and 
%second we can compare how athletes performed at the 2022 championships relative 
%to their national/qualifiers meet. In order to reduce any chances
%of athletes improving reaction time, we can also look at data from qualifying meets.
%Almost every athlete had to qualify by proving they are elite at the national level, 
%usually by coming in at least fourth. Thus, data was compiled on athletes who competed
%at the 2022 World Track and Field Championships on what these athletes also ran 
%at their country's national championship. If there was any argument that athletes
%have improved their reaction time from 2019 to 2022, it should now be considered
%nearly null, as the national competitions took place between June and July 2022 
%and the World Championships were in August. The equipment used to measure reaction
%time cannot be guaranteed to be the same from national to international
%competition, but the time span between meets has been reduced considerably.

@@

There are two types of data that are explored throughout this paper: data from
1999-2022 for every world championship, and data from athletes who competed in
the 2022 World Championships and another competition (either 2019 World 
Championships or a 2022 national competition typically held within three months 
of the 2022 World Championships). 
\eds{is this true? are you still using the 2019 world championships data for the
rank-based analyses, or only the national competitions?}
\of{Yes the ranked based comparison has 2 subsections: 2022 national vs 2022
international and 2019 international vs 2022 international.  Should I instead say
that there are three types of data across 2 sections or something like that?}
The first data set is used for the GLMM analyses described in 
Section~\ref{sec:glmm}, while the second collection of data is used for the 
rank-based comparisons described in Section~\ref{sec:rank}.

@@

\eds{I wonder if this paragraph would be better placed in the introduction?}
\of{I think it could fit in the brief section between the start of the Data section
and the GLMM subsection in the paragraph starting with "There are two types..."}
Something that is extremely important to note in the data is the inconsistency 
of World Athletics in terms of how they penalize false starts.  From 2007--2009,
the IAAF (the former name for World Athletics, and the governing body for the 
World Track and Field Championships) instituted a rule change that allowed one 
warning false start before a sprinter was disqualified \citep{iaaf2009falsestart}. 
This was desirable for World Athletics as false starts can make already long 
track meets more tedious, both for athletes and viewers watching the television 
broadcast.  There were 18 male and 7 female false starts at the 2007 World 
Championships, and 18 male and 7 female starts at the 2009 World Championships. 
Starting in 2011, the rule was scrapped, and the old policy which automatically 
disqualifies runners who false start was reinstated. By returning to the harsher 
policy and cracking down on false starts, World Athletics had reduced men's 
false starts by two thirds in 2011 (6 male and 4 female disqualifications) 
\citep{iaaf2009falsestart}.
%The effect? At the 2011 
%World Championships there were 6 male disqualifications and 4 female 
%disqualifications \citep{iaaf2009falsestart}.  
%One study that looked at different false start rules that IAAF has
%imposed from 1997 to 2009 and found that the reaction times when there was less 
%leniency improved by a statistically significant amount
%\citep{haugen2013effect}. 
\citet{haugen2013effect} examined the effect of different false start
rules that IAAF has imposed from 1997 to 2009 and found statistically 
significant improvement in reaction times under more lenient rules.
  %\eds{I am not sure the previous sentence follows from the one preceding it. Why
% does World Athletics find faster reaction times desirable?  Do you mean that
%they find fewer false starts desirable?}

@@

\subsection{Beyond World Championships}\label{sec:databeyond}
The motivation for looking beyond World Championships data came from an 
exploratory analysis examining how United States athletes reacted at the 
2022 United States Track and Field Championships.
%\eds{be consistent with how you refer to the US championship:
%``United States Track and Field Championships" and ``United States Track and Field 
%Championships" are both being used; please pick one and use that throughout}
%\of{Resolved; changed all USA to United States.}
From June 23-26 2022, the United States held its Track
and Field Championships at Hayward 
Field in Eugene, Oregon to decide who to send to the World Championships 
being held at the same venue in August. %the exact same venue as used 
%for the World Track and Field Championships a month later.  
%Thus, a baseline is able to be established for the four United States athletes who 
Thus, we can establish a baseline for the four United States athletes who 
competed in at least one round of both events: Trey Cunningham, Daniel Roberts, 
Grant Holloway, and Devon Allen. Every athlete reacted faster in all the World 
Track and Field Championships races compared to the United States Track and Field 
Championships races. Devon Allen raced three times at the United States Track and
Field Championships and three times at the World Track and Field Championships. 
His reaction times were substantially faster in the World Track and
Field Championships compared to the United States Track and Field Championships 
as were his
teammates. 
This comparison suggests that the timing system used between the two
meets may have been meaningfully different to the point where Devon Allen was
disqualified more because of faulty equipment rather than because he reacted
too quickly.  Table~\ref{fig:USAvsWorld} highlights the difference in reaction 
times for Devon Allen, Trey Cunningham, Grant Holloway, and Daniel Roberts. 
%``United States" denotes
%the United States Track and Field Championships, ``World" denotes the World Track and Field
%Championships. All numbers listed in the table are the reaction
%time for the respective athletes in seconds.

@@

The %World Championships data and the data eyond the World Championships 
data described in Sections~\ref{sec:dataworld} and~\ref{sec:databeyond} were
analysed with GLMM and rank-based methods, respectively.
\eds{need consistency with ``Championship" or ``Championships - I am not sure 
which one is correct.  I am using Championships (plural) but
change everything to singular if that is preferred}
\of{I believe that championships is correct, I have changed all instances of
championship to championships}

@@

%% In this case, athletes who have more
%% data are generally thought to be faster, as they have made it further in the
%% competition.  Clusters range from two to six, with two indicating that at each
%% competition they only made it to the heats, but a cluster size of six indicates
%% that they made the finals in both competitions.  While the number of times
%% athletes compete is based off their overall time not their reaction time, the
%% two are correlated \citep{delalija2008reaction}.
%% Group is either designated to be 1 or 2, with 1 corresponding to either the
%% national level data or the previous world championships data and 2 corresponding
%% to the 2022 data.

@@

%Citation needed in this section
Since 1985 Seiko Holding Corporations has served every World Athletics 
Championships as the official timer \citep{wa2022seiko}.  Since 1985, the 
technology and the ability
to accurately predict measurements: long jump distances, false starts, total 
time, reaction time, etc. have all dramatically improved.  Seiko did not start 
tracking reaction time as an official measurement until 1999 in the men's and 
women's 100 meter \eds{110 for men?} hurdles. 
Seiko regularly updates their equipment so that they provide cutting edge
technology to the World Track and Field Championships, the highest stakes in the 
world of running outside of the Olympics. Seiko's technology for detecting 
reaction times relies on the pressure that athletes exert on the plate when they 
push off.  Their systems measure the time differential
between when the ``gun" goes off to start the race and when the pressure changes 
\citep{wa2022seiko}.  If an athlete has a reaction time under 0.1 seconds, it 
is deemed a 
false start as it is considered that no athlete can react so quickly 
\citep{Seiko-Timing}.  Thus, a reaction time of for example 0.05, suggests that 
the athlete predicted the gun and it was luck that caused their abnormally high 
time.  At the World Championships level, World Athletics and Seiko want to remove 
that element of luck and thus impose the 0.1 second barrier. In 2013, Seiko 
upgraded their timing equipment for sprinting events (110 meter hurdles falls 
under this category) \citep{wa2013backtage}. Since 1999, the
slowest \eds{highest as in fastest or slowest? Neither seems consistent with 
the boxplots in Figure 1} \of{Resolved} reaction 
times in the men's 110-meter hurdle were recorded in 2013.  That is not to say
 that the higher 
times were caused by Seiko's equipment, but the two may be related.  It is worth 
noting that prior
to 2022, Seiko again upgraded its technology but for its jump management system.
\eds{I would argue that this paragraph should go in the discussion as there are 
no results presented here}

@@

It is worth noting that in the semifinals of the 2022 World Track and
Field Championships, Allen's reaction time was 0.101 which is only 0.001 above
the legal limit. What this suggests is that Allen may have strong reflexes
and be able to react extremely well to the sound of the gun. It seems unlikely 
that Allen would be able to correctly predict the gun with such precision two 
times in a row, which is the exact reason that the 0.1 second reaction time 
disqualification barrier was
imposed in the first place. Thus having a quick reaction time multiple times
may indicate skill rather than luck. Devon 
Allen is a very good athlete, as evidenced by his football career at the 
University of Oregon
and making it onto the Philadelphia Eagles practice squad this past year 
\citep{hurley2022eagles}. The 0.099 reaction time may not have been 
a product of Devon Allen predicting the start of the race but rather a 
combination of a quick reaction and a possibly faulty sensor.
